\Section{conclude}{Conclusion}
We present a new approach to resolving temporal expressions,
	based on synchronous parsing of a fixed grammar with learned parameters
	and a compositional representation of time.
%In addition to providing results competitive with the state of the art,
The system allows for output which captures uncertainty both with respect to 
	the syntactic structure of the phrase and the pragmatic ambiguity of 
	temporal utterances.
We also note that the approach is theoretically better adapted for
	phrases more complex than those found in \tempeval.

Its probabilistic nature gives the system a unique usefulness
	in many tasks.
These include detecting temporal expressions, making probabilistic
	sequence models more practical, or propagating uncertainty as a
	component in larger systems.
Furthermore, the system makes very few language-specific assumptions,
	and the algorithm could be adapted to domains beyond temporal resolution.

We hope to address the task of detection and explore system performance
	on multilingual and complex datasets in future work.

{\footnotesize
\paragraph{\footnotesize Acknowledgements}
The authors would like to thank Valentin Spitkovsky, David McClosky,
	and Angel Chang for valuable discussion and insights.
We gratefully acknowledge the support of the Defense Advanced 
	Research Projects Agency (DARPA) Machine Reading Program under Air 
	Force Research Laboratory (AFRL) prime contract no. FA8750-09-C-0181. 
Any opinions, findings, and conclusions or recommendations expressed 
	in this material are those of the author(s) and do not necessarily 
	reflect the view of DARPA, AFRL, or the US government.
}
